{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-05 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, fixes and changes
>w<, changes at works

        Define the proximal gradient operator by: 
            T_{\beta^{-1}, f, g}(x) &= \hprox_{\beta^{-1}g} \left(

@@

        \begin{theorem}[generic GMAPG LS gradient mapping convergence]

@@

        We introduce two examples variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.  

@@

@@

                \STATE{\textbf{Function ArmijoLS}
                    $(f, g, x, v, L, \alpha, \_, \_)$

@@

@@

                    \textbf{Function ChambBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)

>>>>

        Let $\beta > 0$, we define the proximal gradient operator for all $x \in \RR^n$: 
            T_{\beta^{-1}, f, g}(x) &:= \hprox_{\beta^{-1}g} \left(

@@

        \begin{theorem}[generic GMAPG LS gradient mapping convergence]\;\label{thm:gmapg-generic-gradmap-convergence}\\
            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista}. 
            Let the sequences $(x_k, y_k, v_k)$ satisfy GMAPG (Definition \ref{def:generic-mapg-ls}). 
            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and it is initialized with $x_0=x_0 = T_{1/L_0, f, g}x_{-1}$ for some $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$. 
            Then, the convergence of gradient mapping $\Vert \mathcal G_{1/L_k}(y_k)\Vert$ is described by the sequence $(\beta)_{k \ge 0}$ where $\beta_0 = 1$ and for all $k \ge 1$:
                \beta_k := \prod_{i = 0}^{k - 1}(1 - \alpha_{i + 1}) \max\left(1, \rho_i L_{i + 1}L_i^{-1}\right). 
            It satisfies for all $k \ge 1$ the inequality:
                \Vert \mathcal G_{L_k} y_k\Vert &\le 
                \sqrt{\beta_k}L_k L_0 \left(
                    1 - 
                    \min(\rho_{k - 1}, L_k^{-1} L_{k - 1})^{1/2}
                \right)\Vert x^+ - v_0\Vert. 

@@

            The following intermediate results are in order for the proof. 
                \item[(a)]

@@

        This section introduces two variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls}. 

@@

                    % \textbf{Function ArmijoLS}
                    % $(f, g, x, v, L, \alpha, \_, \_)$
                    \textbf{Function ArmijoLS:}
                    \begin{tabular}{lcl}
                        $f : \RR^n \rightarrow \RR$ && Convex Lipschitz smooth\\ 
                        $g: \RR^n \rightarrow \overline \RR$  &&  Convex function with Proximal operator\\ 
                        $x \in \RR^n$ && Vector\\
                        $v \in \RR^n$ && Vector\\
                        $L \in \RR$ && $L > 0$\\
                        $\alpha \in \RR$  && $\alpha \in (0, 1]$
                    \end{tabular}

@@

                \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + 1} - \alpha^2\right)$.}
                \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+)x$.}
                \STATE{$L^+ := L$. }
                \FOR{$i = 1, 2,\ldots, 53$}
                    \STATE{$L^+ := 2L^+$. }
                    \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$. }
                    \IF{$D_f(x^+, y^+) \le (L^+/2)\Vert x^+ - y^+\Vert^2$}
                    \STATE{$L^+ := 2^{i}L$}
                \STATE{\textbf{Return:} $y^+, x^+, \alpha^+, L^+$}

@@

                    \textbf{Function ChamBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
